# （四）散点图-正常体重指数BMI变化
文献：Accelerated waning of the humoral response to COVID-19 vaccines in obesity，Fig. 4c: Third-dose COVID-19 vaccine-induced immunity in individuals with severe obesity.

```{r}
mydata <- data.frame(
  id = c(1:12, 1:12),
  visit_times = c(rep("V3D28", 12), rep("V3D105", 12)),
  NT50 = c(820, 1160, 5315, 1528, 4010, 3540, 930, 2198, 1700, 940, 3570, 940,
           380, 1010, 5165, 1590, 2810, 1460, 900, 2320, 620, 430, 2690, 560))

```{r}
mydata
# 载入R包
library(ggplot2)


# 作图
```{r}
ggplot(mydata, aes(x = visit_times, y = NT50, group = id)) +
  geom_point(size = 1.5) + # 点
  geom_line(linetype = "dashed") + # 连接线
  geom_hline(yintercept = 10, linetype = "dotted") +
  scale_x_discrete(limits = c("V3D28", "V3D105")) +
  scale_y_log10(breaks = c(1, 10, 100, 1000, 10000, 100000), limits = c(1, 100000), # log10后的y轴
                expand = c(0, 0), labels = c("1", "10", "100", "1,000", "10,000", "100,000")) +
  theme_classic() +
  theme(plot.title = element_text(face = "bold", size = 16, hjust = -0.3),
        plot.subtitle = element_text(size = 14, hjust = 0.5),
        axis.text.x = element_text(size = 11),
        axis.line = element_line(linewidth = 0.2),
        legend.position = "none") +
  labs(title = "c",
       subtitle = "Normal BMI",
       x = "",
       y = expression("NT"["50"]))
```


# （五）热图
文献：Accelerated waning of the humoral response to COVID-19 vaccines in obesity，Fig. 3. Immune response to third (booster) dose COVID-19 vaccination. 

```{r}
# 创建数据
set.seed(1288) # 让随机数据可重复
protein_expression <- matrix(runif(90), ncol = 5)

```{r}
# 修改列和行的名称
colnames(protein_expression) <- paste("Cluster", 1:5, sep = "")
rownames(protein_expression) <- paste("Protein", 1:18, sep = "")


# 转化成matrix格式的数据
mydata <- as.matrix(protein_expression)

# 标签变量
labs <- colnames(mydata)

```{r}
# 查看数据
mydata
heatmap(mydata,
        ColSideColors = c("blueviolet", "orange1", "limegreen", "firebrick1", "dodgerblue3"),
        labCol = "", # 不显示列的label
        add.expr = text(x = seq_along(labs), y = -0.2, srt = 0, # 重新调整列标签的位置和角度
                        labels = labs, xpd = TRUE, cex = 1.5),
        cexRow = 1.5) # 行标签的字体大小
```
